Improving Haskell Theory Exploration

### 2015-11-24 TransferReport/background.tex
Updates

\begin{figure}
  \begin{equation*}
    \begin{split}
      expr\    \rightarrow\ & \texttt{Var}\ id                                       \\
                         |\ & \texttt{Lit}\ literal                                  \\
                         |\ & \texttt{App}\ expr\ expr                               \\
                         |\ & \texttt{Lam}\ \mathcal{L}\ expr                        \\
                         |\ & \texttt{Let}\ bind\ expr                               \\
                         |\ & \texttt{Case}\ expr\ \mathcal{L}\ \left[ alt \right]   \\
      id\      \rightarrow\ & \texttt{Local}\ \mathcal{L}                            \\
                         |\ & \texttt{Global}\ \mathcal{G}                           \\
      literal\ \rightarrow\ & \texttt{LitNum}\ \mathcal{N}                           \\
                         |\ & \texttt{LitStr}\ \mathcal{S}                           \\
      alt\     \rightarrow\ & ( altcon,\ [\mathcal{L}],\ expr )                      \\
      altcon\  \rightarrow\ & \texttt{DataAlt}\ \mathcal{G}                          \\
                         |\ & \texttt{LitAlt}\ literal                               \\
                         |\ & \texttt{Default}                                       \\
      bind\    \rightarrow\ & \texttt{NonRec}\ \mathcal{L}\ expr                     \\
                         |\ & \texttt{Rec}\ [ ( \mathcal{L},\ expr ) ]
    \end{split}
  \end{equation*}
  Where:
  \begin{tabular}[t]{l @{ $=$ } l}
    $\mathcal{S}$ & string literals    \\
    $\mathcal{N}$ & numeric literals   \\
    $\mathcal{L}$ & local identifiers  \\
    $\mathcal{G}$ & global identifiers
  \end{tabular}

@@

We decided to focus our theory exploration research on Haskell as it has mature, state-of-the-art implementations (\qspec{} \citep{QuickSpec} and \hspec{} \citep{claessen2013automating}). This is evident from the fact that the state-of-the-art equivalent for Isabelle/HOL, the \textsc{Hipster} \citep{Hipster} system, is actually implemented by translating to Haskell and invoking \hspec{}.

Haskell is a programming language which is well-suited to research; indeed, this was a goal of the language's creators \citep{marlow2010haskell}. Like most members of the \emph{functional programming} paradigm, Haskell is essentially a variant of $\lambda$-calculus; in fact an intermediate representation of the \textsc{GHC} compiler, known as \emph{GHC Core}, is based on a variant of the polymorphic $\lambda$-calculus known as \fc{}. For simplicity, we will focus on this Core language rather than the relatively large and complex syntax of Haskell proper. For a full treatment of \fc{} and its use in GHC, see \citep[Appendix C]{sulzmann2007system}.

The sub-set of Core we consider is shown in figure \ref{fig:coresyntax}; compared to the full language \footnote{As of GHC version 7.10.2, the latest at the time of writing.} our major changes are to erase types and use a custom representation of names. There are also several other forms of literal (machine words of various sizes, individual characters, etc.) which we omit for brevity, as their treatment is similar to those of strings and numerals.

@@

Although unit testing is the de facto industry standard for quality assurance in non-critical systems, the level of confidence it provides is rather low, and totally inadequate for many (e.g. life-) critical systems. To see why, consider the following Haskell function, along with some unit tests (see \ref{sec:haskell} for more details on Haskell):

@@

We can reduce this bias further through the use of \emph{theory exploration} tools, such as \qspec{} and \hspec{}. These programs \emph{discover} properties of a ``theory'' (e.g. a library), through a combination of brute-force enumeration, random testing and (in the case of \hspec{}) automated theorem proving.\footnote{See section \ref{sec:atp} for more information on automated theorem proving.}

@@

In this work we focus on the problem of \emph{(automated) theory exploration}, which includes the ability to \emph{generate} conjectures about code, to \emph{prove} those conjectures, and hence output \emph{novel} theorems without guidance from the user. The method of conjecture generation is a key characteristic of any theory exploration system, although all existing implementations rely on brute force enumeration to some degree.

@@

\begin{enumerate}
  \item Given a typed signature $\Sigma$ and set of variables $V$, \qspec{} generates a list $terms$ containing the functions and constants from $\Sigma$, the variables from $V$ and type-correct function applications $f(x)$, where $f$ and $x$ are elements of $terms$. To ensure the list is finite, function applications are only nested up to a specified depth (e.g. 3).
  \item The elements of $terms$ are grouped into equivalence classes, based on their type.
  \item Each variable is instantiated to particular value, generated randomly by \qcheck{}.
  \item For each class, the members are compared (using a pre-specified function, such as equality \hs{==}) to see if these instantiations have caused an observable difference between members. If so, the class is split up to separate such members.
  \item The previous steps of variable instantiation and comparison are repeated until the classes stabilise (i.e. no differences have been observed for some specified number of repetitions).
  \item A set of equations are then conjectured, relating each class's members.
\end{enumerate}

Such $conjectures$ can be used in several ways: they can be simplified for direct presentation to the user (by removing any equation which is a can be derived from the others by rewriting), sent to a more rigorous system like \hspec{} or \textsc{Hipster} for proving, or even serve as a background theory for an automated theorem prover \citep{claessen2013automating}.

@@

\begin{multline}
  terms_{\mathbb{N}} = \{0,\ succ,\ plus,\ times,\ x,\ y,\ succ(0),\ succ(x),\ succ(y),\ succ(z), \\
                    plus(0,\blank),\ plus(x, \blank),\ \dots \}
\end{multline}

@@

These terms will be grouped into three classes, for $\mathbb{N}$, $\mathbb{N} \rightarrow \mathbb{N}$ and $\mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$. As the variables $x$, $y$ and $z$ are instantiated to various randomly-generated numbers, these equivalence classes will be divided, until equations such as the following are conjectured (after simplification):

% To reproduce, run 'quickSpec nat' in haskell_example/src/QuickSpecExample.hs
\begin{align*}
                      plus(x, y) &= plus(y, x)
                      plus(x, 0) &= x
             plus(x, plus(y, z)) &= plus(y, plus(x, z))
                     times(x, y) &= times(y, x)
                     times(x, 0) &= 0
           times(x, times(y, z)) &= times(y, times(x, z))
                plus(x, succ(y)) &= succ(plus(x, y))
               times(x, succ(y)) &= plus(x, times(x, y))
            times(x, plus(y, y)) &= times(y, plus(x, x))
  plus(times(x, y), times(x, z)) &= times(x, plus(y, z))
\end{align*}

\qspec{} (and \hspec{}) is also compatible with Haskell's existing testing infrastructure, such that an invocation of \texttt{cabal test} can run these tools alongside more traditional QA tools like \qcheck{}, \textsc{HUnit} and \textsc{Criterion}.

@@

We attempt to mitigate the cost of running \qspec{}, by providing a machine learning layer analogous to that of premise selection in theorem proving. Of particular concern is the set of expressions $exprs$, which grows exponentially as the size of the expressions increases, and hence slows down the rest of the algorithm. Although complete, the current enumeration approach is wasteful: many combinations are unlikely to appear in theorems, which requires careful choice by the user of what to include in the signature. The key idea of premise selection is to make such choices automatically, by only including those expressions which are considered \emph{relevant} to the problem.

\iffalse TODO: Not immediately clear how the problem of reducing the set of expressions relates to premise selection \fi
\iffalse TODO: This detailed comparison with premise selection is opaque without defining/explaining what premise selection is \fi

@@

@@

\subsection{Clustering}
\label{sec:clustering}
% TODO

>>>>

\begin{figure}
  \begin{equation*}
    \begin{split}
      expr\    \rightarrow\ & \texttt{Var}\ id                                       \\
                         |\ & \texttt{Lit}\ literal                                  \\
                         |\ & \texttt{App}\ expr\ expr                               \\
                         |\ & \texttt{Lam}\ \mathcal{L}\ expr                        \\
                         |\ & \texttt{Let}\ bind\ expr                               \\
                         |\ & \texttt{Case}\ expr\ \mathcal{L}\ \left[ alt \right]   \\
                         |\ & \texttt{Type}                                          \\
      id\      \rightarrow\ & \texttt{Local}\ \mathcal{L}                            \\
                         |\ & \texttt{Global}\ \mathcal{G}                           \\
      literal\ \rightarrow\ & \texttt{LitNum}\ \mathcal{N}                           \\
                         |\ & \texttt{LitStr}\ \mathcal{S}                           \\
      alt\     \rightarrow\ & ( altcon,\ [\mathcal{L}],\ expr )                      \\
      altcon\  \rightarrow\ & \texttt{DataAlt}\ \mathcal{G}                          \\
                         |\ & \texttt{LitAlt}\ literal                               \\
                         |\ & \texttt{Default}                                       \\
      bind\    \rightarrow\ & \texttt{NonRec}\ \mathcal{L}\ expr                     \\
                         |\ & \texttt{Rec}\ [ ( \mathcal{L},\ expr ) ]
    \end{split}
  \end{equation*}
  Where:
  \begin{tabular}[t]{l @{ $=$ } l}
    $\mathcal{S}$ & string literals    \\
    $\mathcal{N}$ & numeric literals   \\
    $\mathcal{L}$ & local identifiers  \\
    $\mathcal{G}$ & global identifiers
  \end{tabular}

@@

We decided to focus on theory exploration in the Haskell programming language as it has mature, state-of-the-art implementations (\qspec{} \citep{QuickSpec} and \hspec{} \citep{claessen2013automating}). This is evident from the fact that the state-of-the-art equivalent for Isabelle/HOL, the \textsc{Hipster} \citep{Hipster} system, is actually implemented by translating to Haskell and invoking \hspec{}.

Haskell is well-suited to programming language research; indeed, this was a goal of the language's creators \citep{marlow2010haskell}. Like most members of the \emph{functional programming} paradigm, Haskell is essentially a variant of $\lambda$-calculus, with extra features such as a strong type system and ``syntactic sugar'' to improve readability. For simplicity, we will focus on an intermediate representation of the \textsc{GHC} compiler, known as \emph{GHC Core}, rather than the relatively large and complex syntax of Haskell proper. Core is based on \fc{}, but for our machine learning purposes we are mostly interested in its syntax; for a more thorough treatment of \fc{} and its use in GHC, see \citep[Appendix C]{sulzmann2007system}.

The sub-set of Core we consider is shown in figure \ref{fig:coresyntax}; compared to the full language \footnote{As of GHC version 7.10.2, the latest at the time of writing.} our major changes are to ignore type hints (explicit casts are removed, whilst particular types/kinds/coercions are all represented by \texttt{Type}) and to use a custom representation of names. We also omit several other forms of literal (machine words of various sizes, individual characters, etc.) for brevity, as their treatment is similar to those of strings and numerals.

@@

Although unit testing is the de facto industry standard for quality assurance in non-critical systems, the level of confidence it provides is rather low, and totally inadequate for many (e.g. life-) critical systems. To see why, consider the following Haskell function, along with some unit tests:

@@

We can reduce this bias further through the use of \emph{theory exploration} tools, such as \qspec{} and \hspec{}. These programs \emph{discover} properties of a ``theory'' (e.g. a library), through a combination of brute-force enumeration, random testing and (in the case of \hspec{}) automated theorem proving.

@@

In this work we consider the problem of \emph{(automated) theory exploration}, which includes the ability to \emph{generate} conjectures about code, to \emph{prove} those conjectures, and hence output \emph{novel} theorems without guidance from the user. The method of conjecture generation is a key characteristic of any theory exploration system, although all existing implementations rely on brute force enumeration to some degree.

@@

\begin{enumerate}
  \item Given a typed signature $\Sigma$ and set of variables $V$, \qspec{} generates a list $terms$ containing the functions and constants from $\Sigma$, the variables from $V$ and type-correct function applications $f(x)$, where $f$ and $x$ are elements of $terms$. To ensure the list is finite, function applications are only nested up to a specified depth (by default, 3).
  \item The elements of $terms$ are grouped into equivalence classes, based on their type.
  \item Each variable is instantiated to a particular value, generated randomly by \qcheck{}.
  \item For each class, the members are compared (using a pre-specified function, such as equality \hs{==}) to see if these instantiations have caused an observable difference between members. If so, the class is split up to separate such distinguishable members.
  \item The previous steps of variable instantiation and comparison are repeated until the classes stabilise (i.e. no differences have been observed for some specified number of repetitions).
  \item A set of equations are then conjectured, relating each class's members.
\end{enumerate}

Such $conjectures$ can be used in several ways: they can be simplified for direct presentation to the user (by removing any equation which can be derived from the others by rewriting), sent to a more rigorous system like \hspec{} or \textsc{Hipster} for proving, or even serve as a background theory for an automated theorem prover \citep{claessen2013automating}.

@@

\begin{align*}
  terms_{\mathbb{N}} = [& 0,\ succ,\ plus,\ times,\ x,\ y,\ z,\ succ(0),\ succ(x),\ succ(y), \\
                     & succ(z),\ plus(0,\blank),\ plus(x, \blank),\ \dots ]
\end{align*}

@@

\begin{figure}
  % To reproduce, run 'quickSpec nat' in haskell_example/src/QuickSpecExample.hs
  \begin{align*}
                        plus(x, y) &= plus(y, x)            \\
                        plus(x, 0) &= x                     \\
               plus(x, plus(y, z)) &= plus(y, plus(x, z))   \\
                       times(x, y) &= times(y, x)           \\
                       times(x, 0) &= 0                     \\
             times(x, times(y, z)) &= times(y, times(x, z)) \\
                  plus(x, succ(y)) &= succ(plus(x, y))      \\
                 times(x, succ(y)) &= plus(x, times(x, y))  \\
              times(x, plus(y, y)) &= times(y, plus(x, x))  \\
    plus(times(x, y), times(x, z)) &= times(x, plus(y, z))
  \end{align*}
  \caption{Equations conjectured by \qspec{} for Peano numerals, addition and multiplication; after simplification.}
  \label{fig:qspecresult}
\end{figure}

These terms will be grouped into three classes, one each for $\mathbb{N}$, $\mathbb{N} \rightarrow \mathbb{N}$ and $\mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$. As the variables $x$, $y$ and $z$ are instantiated to various randomly-generated numbers, these equivalence classes will be divided, until eventually the equations in figure \ref{fig:qspecresult} are conjectured.

Although complete, this enumeration approach is wasteful: many terms are unlikely to appear in theorems, which requires careful choice by the user of what to include in the signature. Here we know that addition and multiplication are closely related, and hence obey many algebraic laws. Our machine learning technique aims to predict these kinds of relations between functions, so we can create small signatures which nevertheless have the potential to give rise to many equations.

\qspec{} (and \hspec{}) are also compatible with Haskell's existing testing infrastructure, such that an invocation of \texttt{cabal test} can run these tools alongside more traditional QA tools like \qcheck{}, \textsc{HUnit} and \textsc{Criterion}.

@@

@@

\iffalse

@@

\subsection{Clustering}
\label{sec:clustering}
% TODO
\fi

### 2015-11-24 TransferReport/contributions.tex
Updates

Two simple methods for comparison are to ignore identifiers completely, or to compare them for equality. Neither is completely satisfactory, as the former will \emph{over-estimate} similarity (considering $X$, $Y$ and $Z$ to be the same), whilst the latter will \emph{under-estimate} similarity (considering $X$, $Y$ and $Z$ to be equidistant).

@@

Recurrent clustering tackles this problem in a straightforward way: we look up the expressions \emph{referenced by} each identifier, and use \emph{their} similarity in place of the identifiers'. This gives rise to a recursive process, where feature extraction is interleaved with multiple rounds of clustering. For this recursive process to be well-founded, we impose a topological ordering on expressions based on their dependencies (the expressions they reference). This is slightly complicated in Haskell (compared to Coq, for example), since general recursion is permitted and several mutually-recursive expressions may appear at the same level.

\subsubsection{Algorithm}
\label{algorithm}

\begin{figure}
  \begin{lstlisting}[language=Haskell, xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
    data RoseTree a = Node a [RoseTree a]

    eRT :: [Local] -> [[Global]] -> Expr -> RoseTree Feature
    eRT env db e = case e of
      Var (Global i) -> Node (lookupG db  i) []
      Var (Local  i) -> Node (lookupL env i) []
      Lit (LitNum _) -> Node sLITNUM []
      Lit (LitStr _) -> Node sLITSTR []
      Lam  i  e      -> Node sLAM [eRT (i:env) db e]
      App  e1 e2     -> Node sAPP [eRT    env  db e1,
                                   eRT    env  db e2]
      Let  bs e      -> Node sLET (map (bRT (ids bs:env) db) bs ++
                                        eRT (ids bs:env) db  e
      Case e i alts  -> Node sCASE (eRT    env  db  e :
                               map (aRT (i:env) db) alts)

    aRT :: [Local] -> [[Global]] -> Alt -> RoseTree Feature
    aRT env db alt = case alt of
      (DataAlt _, vs, e) -> eRT (vs ++ env) db e
      (LitAlt  _, _,  e) -> eRT env db e
      (Default,   _,  e) -> eRT env db e

    bRT :: [Local] -> [[Global]] -> Bind -> RoseTree Feature
    bRT env db b = case b of
      NonRec i e -> eRT env db e
      Rec es     -> Node sREC (map (eRT env db . snd) es)

    level :: Int -> RoseTree Feature -> [Feature]
    level 0 (Node x xs) = [x]
    level n (Node x xs) = concatMap (level (n-1)) xs

    rt :: [[Global]] -> Expr -> [Feature]
    rt db e = concat (pad cols (map (`level` eRT [] db e) [0..rows]))

    recurrentCluster :: [[(Global, Expr)]] -> [[Global]]
    recurrentCluster = go ([],[])
      where go (fs, db) []       = db
            go (fs, db) (es:ess) = let fs' = fs ++ map (extract db) es
                                       db' = kMeans fs'
                                    in go (fs', db') ess
            extract db (i, e) = (i, rt db e)
  \end{lstlisting}
  \caption{Feature extraction for Haskell Core. We send named expressions to \hs{recurrentCluster}, topologically sorted: if an element contains multiple \hs{(Global, Expr)} pairs, they are mutually-recursive. Syntax trees are first converted into \hs{RoseTree}s of \hs{Feature}s, these trees are converted to matrices, then flattened into feature vectors, then \hs{kMeans} clusters the feature vectors. The result is a list of clusters, naming their elements. More details are given in \S \ref{algorithm}.}
  \label{featureextractionalgorithm}
\end{figure}

Our feature extraction algorithm is given in figure \ref{featureextractionalgorithm}. Here we highlight some key features:

\begin{itemize}
  \item Since they are comparatively rare, we ignore the particular value of each literal.
  \item Since we are currently focused on expressions, we ignore particular data constructors and types.
  \item The \hs{lookupL} and \hs{lookupG} functions return the index containing their argument, if found. In the case of \hs{lookupL}, this acts as a de Bruijn index to give alpha-equivalent terms equal feature vectors. For \hs{lookupG}, this is the ID of the cluster it appears in; this ensures that references to similar expressions result in similar features.
  \item \hs{lookupL} and \hs{lookupG} return a sentinel value \hs{sUNKNOWN} if the given ID is not found. In practice, this only occurs for global, mutually-recursive references, since the toplogical sort will populate the \hs{db} with all other global identifiers, and local identifiers which don't occur in the environment would be rejected as invalid Haskell before the translation to Core.
  \item The \hs{Feature} type is abstract, but in practice it will be \hs{Float}.
  \item Our algorithm contains several parameters, including \hs{rows} and \hs{cols} which determine how to truncate the matrices (defaults are 30). The \hs{kMeans} function also contains a parameter for the cluster number; we set this as $\sqrt{n}$ where $n$ is the number of feature vectors being clustered.
\end{itemize}

@@

\begin{itemize}
  \item Although they are values, we cannot distinguish between data constructors, other than using exact equality.
  \item Since Core uses a single \texttt{Lam} abstraction for both value- and type-level parameters, we cannot completely erase type-level parameters unless they are fully applied. This can cause a function's Core arity to be greater than its Haskell arity.
\end{itemize}

>>>>

Two possible methods for comparison are to ignore identifiers completely, or to compare them for equality. Neither is completely satisfactory, as the former will \emph{over-estimate} similarity (considering $X$, $Y$ and $Z$ to be the same), whilst the latter will \emph{under-estimate} similarity (considering $X$, $Y$ and $Z$ to be equidistant).

@@

Recurrent clustering tackles this problem in a simple way: we look up the expressions \emph{referenced by} each identifier, and use \emph{their} similarity in place of the identifiers'. This gives rise to a recursive process, where feature extraction is interleaved with multiple rounds of clustering. For this recursive process to be well-founded, we impose a topological ordering on expressions based on their dependencies (the expressions they reference). This is slightly complicated in Haskell (compared to Coq, for example), since general recursion is permitted and several mutually-recursive expressions may appear at the same level.

\subsubsection{Algorithm}
\label{sec:algorithm}

Our algorithm proceeds in several stages. At the top level, we send named expressions to \hs{recurrentCluster}, topologically sorted: if an element contains multiple \hs{(Global, Expr)} pairs, they are mutually-recursive:

\begin{haskell}
recurrentCluster :: [[(Global, Expr)]] -> [[Global]]
recurrentCluster = go ([],[])
  where go (fs, db) []       = db
        go (fs, db) (es:ess) = let fs' = fs ++ map (extract db) es
                                   db' = kMeans fs'
                                in go (fs', db') ess
        extract db (i, e) = (i, rt db e)
\end{haskell}

The overall result of the \hs{recurrentCluster} function is a list of clusters, containing the IDs of their elements. These are obtained by interleaving clustering (the \hs{kMeans} function) and feature extraction (the \hs{rt} function).

The feature extraction itself contains two parts: first, syntax trees matching the grammar in figure \ref{fig:coresyntax} are converted into \hs{RoseTree}s with features (\hs{Float}s) on their \hs{Node}s:

\begin{haskell}
data RoseTree = Node Feature [RoseTree]

eRT :: [Local] -> [[Global]] -> Expr -> RoseTree
eRT env db e = case e of
  ...
\end{haskell}

The easiest branches to handle are literals and types, which we represent using particular feature values (\hs{sLITNUM}, \hs{sLITSTR} and \hs{sTYPE}):

\begin{haskell}
  Lit (LitNum _) -> Node sLITNUM []
  Lit (LitStr _) -> Node sLITSTR []
  Type           -> Node sTYPE   []
\end{haskell}

Function application simply recurses into both sub-expressions:

\begin{haskell}
  App e1 e2 -> Node sAPP [eRT env db e1,
                          eRT env db e2]
\end{haskell}

To look up variables locally and globally, we use the \hs{lookupL} and \hs{lookupG} functions, respectively. These return the index containing their argument, if found. In the case of \hs{lookupL}, this acts as a de Bruijn index to give alpha-equivalent terms equal feature vectors. For \hs{lookupG}, this is the ID of the cluster it appears in; this ensures that references to similar expressions result in similar features:

\begin{haskell}
  Var (Global i) -> Node (lookupG db  i) []
  Var (Local  i) -> Node (lookupL env i) []
\end{haskell}

Finally, when we traverse binders we must extend the environment \hs{env}:

\begin{haskell}
  Lam  i  e     -> Node sLAM [eRT (i:env) db e]
  Let  bs e     -> Node sLET (map (bRT (ids bs:env) db) bs ++
                                   eRT (ids bs:env) db  e
  Case e i alts -> Node sCASE (eRT    env  db  e :
                          map (aRT (i:env) db) alts)
\end{haskell}

Patterns and bindings are handled in a similar way:

\begin{haskell}
aRT :: [Local] -> [[Global]] -> Alt -> RoseTree
aRT env db alt = case alt of
  (DataAlt _, vs, e) -> eRT (vs ++ env) db e
  (LitAlt  _, _,  e) -> eRT env db e
  (Default,   _,  e) -> eRT env db e

bRT :: [Local] -> [[Global]] -> Bind -> RoseTree
bRT env db b = case b of
  NonRec i e -> eRT env db e
  Rec es     -> Node sREC (map (eRT env db . snd) es)
\end{haskell}

The result of \hs{eRT} is a \hs{RoseTree} whose branching structure mimics that of our original expression. We next need to convert this to a \emph{matrix} of features, which we do by converting each level of the \hs{RoseTree} into a row of the matrix (using \hs{pad} to ensure a consistent size). Finally we turn the matrix into a \emph{feature vector} by concatenating the rows:

\begin{haskell}
level :: Int -> RoseTree -> [Feature]
level 0 (Node x xs) = [x]
level n (Node x xs) = concatMap (level (n-1)) xs

rt :: [[Global]] -> Expr -> [Feature]
rt db e = concat (pad cols (map (`level` eRT [] db e) [0..rows]))
\end{haskell}

Notice that this algorithm contains several parameters, including \hs{rows} and \hs{cols} which determine how to truncate the matrices (defaults are 30). The \hs{kMeans} function also contains a parameter for the cluster number; we set this as $\sqrt{n}$ where $n$ is the number of feature vectors being clustered.

@@

\begin{itemize}
  \item Although they are values, we cannot distinguish between data constructors, other than using exact equality.
  \item Since Core uses a single \texttt{Lam} abstraction for both value- and type-level parameters, we cannot always distinguish between them. This can cause a function's Core arity to be greater than its Haskell arity.
\end{itemize}
